DeepPicar: A Low-cost Deep Neural Network-based Autonomous Car

### 2018-04-17 paper/evaluation-drampart.tex
Combine Figures 14 and 15

\begin{figure}[h]
  \centering
  \includegraphics[width=.45\textwidth]{figs/memguard_bandwidth}
  \caption{Timing impact of co-scheduling memory intensive read
co-runners when memory bandwidth throttling is enabled. }
  \label{fig:memguard_bandwidth}
\end{figure}

\begin{figure}[h]
  \centering
  \includegraphics[width=.45\textwidth]{figs/memguard_bwwrite}
  \caption{Timing impact of co-scheduling memory intensive write
co-runners when memory bandwidth throttling is enabled. }
  \label{fig:memguard_bwwrite}
\end{figure}

We also test the performance of the model in the presence of three
memory intensive read and write benchmarks to determine the effects of 
limiting the memory bandwidth of the co-runners. For each of the 
experiments, we give the model's core, Core 0, a constant 1000 MB/s 
memory bandwidth reservation size, and then vary the amount of bandwidth 
the co-runners' cores receive. For read co-runners, we give them an initial
reservation size of 500 MB/s, and decrease that to a minimum of 100 MB/s.
In the case of write co-runners, MemGuard accounts for L2 refills but not
write-backs, so each benchmark would effectively have twice the bandwidth
of their reservation size. Due to this, we give write co-runners an initial 
reservation size of 250 MB/s and decrease it to a minimum of 50 MB/s.
The results can be see in Figures \ref{fig:memguard_bandwidth} and
\ref{fig:memguard_bwwrite}. When less memory bandwidth is given to 
the both the  read and write co-runners, the performance of the model 
improves. 
%% In the case of one co-runner, the performance of the model remains 
%% constant even as the reservation sizes are decreased, however, it 
%% still improves compared to when throttling wasn't enabled. 
In both cases, when the co-runners were given a minimal reservation size,
the performance of the model was much closer to its solo execution time.
This is especially noteworthy when write co-runners were present, as the 
model didn't suffer the same 11.6X slowdown that was seen without
bandwidth throttling enabled. 
%% When memory intensive Bandwidth benchmarks were present, model performance
%% improved, to a notable extent, through the use of memory bandwidth 
%% throttling on the co-runners. 
Since this would not be the case if the 
model was memory insensitive, we find that the model is memory 
dependent in the presence of co-runners.

>>>>

\begin{figure}[h]
  \centering
  \includegraphics[width=.45\textwidth]{figs/memguard_bandwidth}
  \caption{Timing impact of co-scheduling memory intensive
co-runners when memory bandwidth throttling is enabled. }
  \label{fig:memguard_bandwidth}
\end{figure}

%% \begin{figure}[h]
%%   \centering
%%   \includegraphics[width=.45\textwidth]{figs/memguard_bwwrite}
%%   \caption{Timing impact of co-scheduling memory intensive write
%% co-runners when memory bandwidth throttling is enabled. }
%%   \label{fig:memguard_bwwrite}
%% \end{figure}

We also test the performance of the model in the presence of three
memory intensive read and write benchmarks to determine the effects of 
limiting the memory bandwidth of the co-runners. For each of the 
experiments, we give the model's core, Core 0, a constant 1000 MB/s 
memory bandwidth reservation size, and then vary the amount of bandwidth 
the co-runners' cores receive. For read co-runners, we give them an initial
reservation size of 500 MB/s, and decrease that to a minimum of 100 MB/s.
In the case of write co-runners, MemGuard accounts for L2 refills but not
write-backs, so each benchmark would effectively have twice the bandwidth
of their reservation size. Due to this, we give write co-runners an initial 
reservation size of 250 MB/s and decrease it to a minimum of 50 MB/s, but
their effective bandwidths are the same as the read co-runners.
The results can be see in Figures \ref{fig:memguard_bandwidth}. 
When less memory bandwidth is given to both the read and write 
co-runners, the performance of the model improves. 
%% In the case of one co-runner, the performance of the model remains 
%% constant even as the reservation sizes are decreased, however, it 
%% still improves compared to when throttling wasn't enabled. 
In both cases, when the co-runners were given a minimal reservation size,
the performance of the model was much closer to its solo execution time.
This is especially noteworthy when write co-runners were present, as the 
model didn't suffer the same 11.6X slowdown that was seen without
bandwidth throttling enabled. 
%% When memory intensive Bandwidth benchmarks were present, model performance
%% improved, to a notable extent, through the use of memory bandwidth 
%% throttling on the co-runners. 
Since this would not be the case if the 
model was memory insensitive, we find that the model is memory 
dependent in the presence of co-runners.
